---
title: "on-off-kinetics-analysis"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{on-off-kinetics-analysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(nirsdexata)
```

Read in NIRS data.
```{r}
rawdata <- read_nirs(read_nirs_example("on_off_kinetics.txt"))
```

The `rawdata` object is a list and can be interacted with like a list. The `data` slot contains the raw data, read in exactly from the file.

```{r}
head(rawdata$data)
```

The `info` slot contains all information about the measurement as an `info` object, which is a list. The `info` object can be edited. See the \\TODO add thing to get to rd page for the info object.
```{r}
rawdata$info$subj_info$subj_id <- "ID_1"
rawdata$info$meas_id <- "0"
```

## Annotating Data using Info

There are two slots in info that are useful for data annotations. Use the `rawdata$info$bads` slot to list columns that should be removed from analysis. 

```{r}
rawdata$info$bads <- c("TSIFF")
```

Use the `rawdata$info$bounds$removed` to list the sample numbers of data rows that should be removed from analysis. 

```{r}
rawdata$info$bounds$removed <- c()
```

```{r}
rawdata$info$bounds$meas_start <- {startmin} * 60 + {startsec}
rawdata$info$bounds$meas_end <- 960
```

## Interactive Plotting

The interactive plotting function will open a panel displaying the data.

Brush points to select them.
Click the `Remove` button to remove all selected values. Click `Reset` to undo all selections.
Double click to zoom to the area selected with the brush. Double click again to zoom back out. 

When you have removed all data you wish from analysis, click `Done` and the function will save your selections in `info`. 
```{r}
rawdata <- plot_rawdata(rawdata)
```


Static plot of on/off kinetics
```{r}
ook_plot(rawdata)
```


Run asymptotic models and get steady state values. 
```{r}
models <- analysis(rawdata)
```

Plot regression results. 
```{r}
plot_regressions(models)
```

View regression coefficients. 
```{r}
models$coefs
```




